### 2014-04-24 Response_to_R0_Reviews.tex

    The following text has been added to Section III(C):

    \input{arfi_normalization}

    \item \textit{Pg 8 lines 205-214 describe that both B-Mode (for prostate
            capsule) and ARFI (for CG) data were used for segmentation.  First,
            how were these data combined?  Second, the use of B-Mode
            segmentation in addition to ARFI is not clearly specified in the
            titles, text and figures.  For example, in Table III, was the total
            volume calculation a result of both ARFI and B-Mode segmentations?
            In that case, the title and column labels describing "ARFI" total
            volume are confusing because they imply that the B-Mode
            segmentation data were not used.  The same is true for the other
            tables, figures, text, and the main Title of the manuscript.  If I
            understand correctly that B-Mode data were important to the overall
            total volume segmentation, then it would be appropriate to better
            clarify this point.  The point is currently confused by the main
            manuscript title, text and figures that generally refer to "ARFI"
            performance.  I believe the authors try to indicate that both
            B-Mode and ARFI data are used for the segmentation by referring to
            the "ultrasound" imaging performance, as in "… with a mean
            overestimation of of 16.82 ± 22.45\% by ultrasound imaging compared
            to MR volumes (Figure 6(b))." (pg 9 line 225), but this reader did
            not immediately appreciate that "ultrasound" referred to combined
            B-mode and ARFI segmentation as opposed to ARFI alone, and the
            "ARFI" labels throughout the rest of the text, tables, titles, and
            figures further confused this point.}

    This comment is greatly appreciated since the use of both B-mode and ARFI
    imaging for each segmentation was an important part of our methodology, and
    we (1) did not do enough to emphasize this point, and (2) confused matters
    by refering to `ARFI' exclusively in the results.  With respect to how the
    data were combined, we have added the following text to the manuscript
    (Section III(E.2)):

    \input{bmode_arfi_coregistered}

    We also agree that our exclusive use of 'ARFI' for many of the tables,
    figures, manuscript title, and text was confusing, so we have updated all
    references to appropriate include B-mode when appropriate (not delineated
    here in the response due to the number of instances that were edited, but
    all manuscript changes are indicated in \textbf{bold} typeface).  The title
    of the manuscript has also been updated to reflect the importance of B-mode
    imaging in this process, and the abstract and conclusions have also been
    explicitely updated to include the fact that B-mode and ARFI imaging data
    were used in this study.

### 2014-04-24 abstract.tex
corrected complement grammar
updated text to explicitely state that B-mode images were used with ARFI images for all of the total gland / capsule approximations

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second-leading cause of cancer-related death.
Multi-parametric Magnetic Resonance Imaging (mpMRI) has gained recent
popularity to characterize PCa.  ARFI imaging has the potential to aid PCa
diagnosis and management by using tissue stiffness to evaluate prostate zonal
anatomy and lesions.  MR and ARFI \invivo imaging datasets were compared to one
another and with gross pathology measurements made immediately after radical
prostatectomy.  Images were manually segmented in 3D Slicer to delineate the
central gland (CG) and prostate capsule, and 3D models were rendered to
evaluate zonal anatomy dimensions and volumes.  Both imaging modalities showed
good correlation between estimated organ volume and gross pathologic weights.
Ultrasound and MR total prostate volumes were well-correlated (R$^2$ =
\MRarfiVolTotalRsq), but ARFI images yielded prostate volumes that were larger
(\MRarfiVolTotalMeanDiff\% $\pm$ \MRarfiVolTotalStdDiff\%) than MR images, due
to overestimation of the lateral dimension (\ARFImrTotalLatLatMeanPct $\pm$
\ARFImrTotalLatLatStdPct\%), with less significant differences in the other
dimensions (\ARFImrTotalAntPostMeanPct $\pm$ \ARFImrTotalAntPostStdPct\%,
anterior-to-posterior, and \ARFImrTotalApexBaseMeanPct $\pm$
\ARFImrTotalApexBaseStdPct\%, apex-to-base).  ARFI and MR CG volumes were also
well-correlated (R$^2$ = \MRarfiVolCentralRsq).  CG volume differences were
attributed to ARFI underestimation of the apex-to-base axis
(\ARFImrCentralApexBaseMeanPct $\pm$ \ARFImrCentralApexBaseStdPct\%), and ARFI
overestimation of the lateral dimension (\ARFImrCentralLatLatMeanPct $\pm$
\ARFImrCentralLatLatStdPct\%).  ARFI imaging yielded prostate volumes and
dimensions that were well-correlated with MR T2WI estimates, with biases in the
lateral dimension due to poor contrast caused by peri-prostatic fat.  ARFI
imaging is a promising low-cost, portable, real-time modality that can
compliment mpMRI for PCa diagnosis, treatment planning and management.

>>>>

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second-leading cause of cancer-related death.
Multi-parametric Magnetic Resonance Imaging (mpMRI) has gained recent
popularity to characterize PCa.  ARFI imaging has the potential to aid PCa
diagnosis and management by using tissue stiffness to evaluate prostate zonal
anatomy and lesions.  MR and \textbf{B-mode/}ARFI \invivo imaging datasets were
compared to one another and with gross pathology measurements made immediately
after radical prostatectomy.  Images were manually segmented in 3D Slicer to
delineate the central gland (CG) and prostate capsule, and 3D models were
rendered to evaluate zonal anatomy dimensions and volumes.  Both imaging
modalities showed good correlation between estimated organ volume and gross
pathologic weights.  Ultrasound and MR total prostate volumes were
well-correlated (R$^2$ = \MRarfiVolTotalRsq), but \textbf{B-mode} images
yielded prostate volumes that were larger (\MRarfiVolTotalMeanDiff\% $\pm$
\MRarfiVolTotalStdDiff\%) than MR images, due to overestimation of the lateral
dimension (\ARFImrTotalLatLatMeanPct $\pm$ \ARFImrTotalLatLatStdPct\%), with
less significant differences in the other dimensions
(\ARFImrTotalAntPostMeanPct $\pm$ \ARFImrTotalAntPostStdPct\%,
anterior-to-posterior, and \ARFImrTotalApexBaseMeanPct $\pm$
\ARFImrTotalApexBaseStdPct\%, apex-to-base).  ARFI and MR CG volumes were also
well-correlated (R$^2$ = \MRarfiVolCentralRsq).  CG volume differences were
attributed to ARFI underestimation of the apex-to-base axis
(\ARFImrCentralApexBaseMeanPct $\pm$ \ARFImrCentralApexBaseStdPct\%), and ARFI
overestimation of the lateral dimension (\ARFImrCentralLatLatMeanPct $\pm$
\ARFImrCentralLatLatStdPct\%).  B-mode/ARFI imaging yielded prostate volumes
and dimensions that were well-correlated with MR T2WI estimates, with biases in
the lateral dimension due to poor contrast caused by peri-prostatic fat.
\textbf{B-mode combined with} ARFI imaging is a promising low-cost, portable,
real-time modality that can complement mpMRI for PCa diagnosis, treatment
planning and management.

### 2014-04-24 arfi_methods.tex
updated text to explicitely state that B-mode images were used with ARFI images for all of the total gland / capsule approximations

\subsection{ARFI Imaging}
Experimental ARFI imaging data were acquired using a modified Siemens Acuson
SC2000\texttrademark~ultrasound scanner (Siemens Healthcare, Ultrasound Business Unit,
Mountain View, CA, USA) and the \textbf{side-fire array of an Acuson ER7B
endorectal transducer}.  The ARFI imaging sequence was comprised of
standard B-mode ultrasonic imaging, or tracking beams, and pushing beams. For
each lateral location, two pre-push reference images were acquired, then three
300 cycle pushing pulses were transmitted in rapid succession, focused at 30
mm, 22.5 mm, and 15 mm, respectively, and finally the response of the tissue
was tracked for up to 6 ms at a PRF of 8kHz. This pushing strategy is similar to
what has been published by Bercoff \etal~\cite{Bercoff2004}. The 30 mm and 22.5
mm foci pushing pulses were transmitted at 4.6 MHz with a F/2 geometry and the
15 mm focus pushing pulse was transmitted at 5.4 MHz with a F/2.35 geometry to
maintain the same beamwidth (0.67 mm) throughout the region of excitation. A
total of 82 lateral locations were interrogated to cover the 55 mm field of
view, translating 0.67 mm laterally per location.

>>>>

\subsection{B-mode/ARFI Imaging}
Experimental \textbf{B-mode and} ARFI imaging data were acquired using a modified Siemens Acuson
SC2000\texttrademark~ultrasound scanner (Siemens Healthcare, Ultrasound Business Unit,
Mountain View, CA, USA) and the \textbf{side-fire array of an Acuson ER7B
endorectal transducer}.  The ARFI imaging sequence was comprised of
standard B-mode ultrasonic imaging, or tracking beams, and pushing beams. For
each lateral location, two pre-push reference images were acquired, then three
300 cycle pushing pulses were transmitted in rapid succession, focused at 30
mm, 22.5 mm, and 15 mm, respectively, and finally the response of the tissue
was tracked for up to 6 ms at a PRF of 8kHz. This pushing strategy is similar to
what has been published by Bercoff \etal~\cite{Bercoff2004}. The 30 mm and 22.5
mm foci pushing pulses were transmitted at 4.6 MHz with a F/2 geometry and the
15 mm focus pushing pulse was transmitted at 5.4 MHz with a F/2.35 geometry to
maintain the same beamwidth (0.67 mm) throughout the region of excitation. A
total of 82 lateral locations were interrogated to cover the 55 mm field of
view, translating 0.67 mm laterally per location.

### 2014-04-24 conclusions.tex
updated text to explicitely state that B-mode images were used with ARFI images for all of the total gland / capsule approximations

\section{Conclusions}
The delineation of prostate zonal anatomy in ARFI images has been compared with
the established methods for identifying zonal anatomy using MR T2W images.
Both imaging modalities showed moderate correlations between estimated organ
volume and gross pathologic weights, and ARFI:MR total prostate gland volumes
were well-correlated (R$^2$ = \MRarfiVolTotalRsq), but ARFI images yielded
prostate volumes that were, on average, larger (\MRarfiVolTotalMeanDiff\%~$\pm$
\MRarfiVolTotalStdDiff\%) than MR images, primarily due to over-estimation of
the lateral dimension of the prostate total gland (\ARFImrTotalLatLatMeanPct~
$\pm$ \ARFImrTotalLatLatStdPct\%), while differences in the other dimensions
were less significant contributors (\ARFImrTotalAntPostMeanPct~$\pm$
\ARFImrTotalAntPostStdPct\%~and \ARFImrTotalApexBaseMeanPct~$\pm$
\ARFImrTotalApexBaseStdPct\%).  The central zone volumes of ARFI and MR images
were also well-correlated (R$^2$ = \MRarfiVolCentralRsq), with minimal volume
bias between the imaging modalities, but significant variability case-to-case
(\MRarfiVolCentralMeanDiff~$\pm$ \MRarfiVolCentralStdDiff\%).  Central zone
volume differences were, again, strongly attributed to over-estimation of the
lateral dimension (\ARFImrCentralLatLatMeanPct~$\pm$
\ARFImrCentralLatLatStdPct\%), with a significant underestimation of the
apex-to-base dimension (\ARFImrCentralAntPostMeanPct~$\pm$
\ARFImrCentralAntPostStdPct\%).  Strong variability in CG volumes is believed
to be related to the extent of BPH for select cases.  Overall, ARFI imaging of
the prostate yielded prostate volumes and dimensions that were correlated with
MR T2WI estimates, with differences in the lateral and apex-to-base dimensions.
Poor image contrast between the prostate and peri-prostatic fat may be one
cause of these differences.  ARFI imaging is a promising low-cost, real-time
imaging modality that can compliment MR imaging for diagnosis, treatment
planning and management of PCa.

>>>>

\section{Conclusions}
The delineation of prostate zonal anatomy in \textbf{B-mode/}ARFI images has
been compared with the established methods for identifying zonal anatomy using
MR T2W images.  Both imaging modalities showed moderate correlations between
estimated organ volume and gross pathologic weights, and \textbf{B-mode}:MR
total prostate gland volumes were well-correlated (R$^2$ = \MRarfiVolTotalRsq),
but ARFI images yielded prostate volumes that were, on average, larger
(\MRarfiVolTotalMeanDiff\%~$\pm$ \MRarfiVolTotalStdDiff\%) than MR images,
primarily due to over-estimation of the lateral dimension of the prostate total
gland (\ARFImrTotalLatLatMeanPct~ $\pm$ \ARFImrTotalLatLatStdPct\%), while
differences in the other dimensions were less significant contributors
(\ARFImrTotalAntPostMeanPct~$\pm$ \ARFImrTotalAntPostStdPct\%~and
\ARFImrTotalApexBaseMeanPct~$\pm$ \ARFImrTotalApexBaseStdPct\%).  The central
gland volumes of ARFI and MR images were also well-correlated (R$^2$ =
\MRarfiVolCentralRsq), with minimal volume bias between the imaging modalities,
but significant variability case-to-case (\MRarfiVolCentralMeanDiff~$\pm$
\MRarfiVolCentralStdDiff\%).  Central gland volume differences were, again,
strongly attributed to over-estimation of the lateral dimension
(\ARFImrCentralLatLatMeanPct~$\pm$ \ARFImrCentralLatLatStdPct\%), with a
significant underestimation of the apex-to-base dimension
(\ARFImrCentralAntPostMeanPct~$\pm$ \ARFImrCentralAntPostStdPct\%).  Strong
variability in CG volumes is believed to be related to the extent of BPH for
select cases.  Overall, B-mode/ARFI imaging of the prostate yielded prostate
volumes and dimensions that were correlated with MR T2WI estimates, with
differences in the lateral and apex-to-base dimensions.  Poor image contrast
between the prostate and peri-prostatic fat may be one cause of these
differences.  \textbf{B-mode imaging combined with} ARFI imaging is a promising
low-cost, real-time imaging modality that can complement MR imaging for
diagnosis, treatment planning and management of PCa.

### 2014-04-24 disc_arfi_mr.tex
updated text to explicitely state that B-mode images were used with ARFI images for all of the total gland / capsule approximations

\subsection{ARFI and MR T2WI Agreement}
This study demonstrated that ARFI imaging delineates zonal anatomy of the
prostate well when compared to MR T2WI with only slight overestimation of ARFI
total and central gland volume (Figure~\ref{fig:mr_arfi_volumes}).
Establishing accurate delineation of the prostate's zonal anatomy is important
because PCa has strong correlations with location in the prostate, specifically
in the peripheral zone, and accurate capsule delineation will facilitate
future efforts to register 3D imaging datasets between ARFI and MR imaging.

We did not expect perfect agreement between MR and ARFI imaging volume or
tri-axial dimensions since each modality applies a different amount of external
compression to the rectal wall, which then deforms the prostate.  The
endorectal coil places pressure on the prostate that is dependent on the
patient's anatomy and overall prostate size, while pressure on the prostate
during ultrasound imaging is modulated by the urologist when the transducer
rotation apparatus is locked into position prior to imaging.  The differential
deformation of the prostate can be easily visualized during the transducer
alignment process during ultrasound imaging.  It was our goal to apply as
little pressure while still maintaining uniform contact throughout the
ultrasound image acquisition. This is critical since poor acoustic coupling to
the prostate through the rectal wall can greatly diminish ARFI image
displacement SNR.

The lateral boundaries of the prostate in the U/S dataset were overestimated
relative to MR T2WI, increasing ARFI total volume relative to MR. The lateral
overestimation was a result of poor contrast between the PZ and peri-prostatic
fat in the B-mode images, and image decimation along the lateral dimension in
both ARFI and B-mode images. Without image decimation, the elevation and axial
orthogonal planes can be used to correct errors introduced by the poor contrast
between the PZ and peri-prostatic fat. However, with image decimation,
segmentation changes in the elevation and axial orthogonal planes were limited
to the lower bound on the model precision of, again, $\sim$3 mm.  While reduced
decimation could improve the precision of the lateral measurements, this would
have introduced significant overhead in the manual segmentation process, with
diminishing returns given the spatial smoothing of the modeling algorithms that
were utilized.

The anterior aspect of the prostate can also be challenging to delineate,
especially in large prostates, where SNR decreases with increasing depth away
from our rectal wall imaging surface and MR images suffer from gland
heterogeneity in this region~\cite{Gupta2013}, though we had good agreement
between ARFI and MR T2W images in the anterior-to-posterior dimension
(Figure~\ref{fig:mr_arfi_path_axes}(b), Table~\ref{tab:mr_arfi_axes_error}).

ARFI imaging consistently underestimated the extent of the prostate capsule and
central gland apex-to-base dimension relative to MR T2WI
((Figure~\ref{fig:mr_arfi_path_axes}(c), Table~\ref{tab:mr_arfi_axes_error}).
In fact, it is likely the degree of ARFI underestimation relative to the actual
apex-to-base prostate length is even greater than suggested by the MR
comparison as this was the dimension with the worst spatial resolution in MR
imaging, with a typical MR T2WI slice thickness of $\sim$3 mm for these
studies.  While higher-resolution MR images could be obtained and analyzed for
more precise comparisons in this imaging dimension, such data were not available
for this study.

>>>>

\subsection{B-mode/ARFI and MR T2WI Agreement}
This study demonstrated that \textbf{B-mode/}ARFI imaging delineates zonal
anatomy of the prostate well when compared to MR T2WI with only slight
overestimation of \textbf{B-mode} total and \textbf{ARFI} central gland volume
(Figure~\ref{fig:mr_arfi_volumes}).  Establishing accurate delineation of the
prostate's zonal anatomy is important because PCa has strong correlations with
location in the prostate, specifically in the peripheral zone, and accurate
capsule delineation will facilitate future efforts to register 3D imaging
datasets between ARFI and MR imaging.

We did not expect perfect agreement between MR and \textbf{ultrasound} imaging
volumes or tri-axial dimensions since each modality applies a different amount
of external compression to the rectal wall, which then deforms the prostate.
The endorectal coil places pressure on the prostate that is dependent on the
patient's anatomy and overall prostate size, while pressure on the prostate
during ultrasound imaging is modulated by the urologist when the transducer
rotation apparatus is locked into position prior to imaging.  The differential
deformation of the prostate can be easily visualized during the transducer
alignment process during ultrasound imaging.  It was our goal to apply as
little pressure while still maintaining uniform contact throughout the
ultrasound image acquisition. This is critical since poor acoustic coupling to
the prostate through the rectal wall can greatly diminish ARFI image
displacement SNR.

The lateral boundaries of the prostate in the \textbf{ultrasound} dataset were
overestimated relative to MR T2WI, increasing \textbf{B-mode} total volume
relative to MR. The lateral overestimation was a result of poor contrast
between the PZ and peri-prostatic fat in the B-mode images, and image
decimation along the lateral dimension in both ARFI and B-mode images. Without
image decimation, the elevation and axial orthogonal planes can be used to
correct errors introduced by the poor contrast between the PZ and
peri-prostatic fat. However, with image decimation, segmentation changes in the
elevation and axial orthogonal planes were limited to the lower bound on the
model precision of, again, $\sim$3 mm.  While reduced decimation could improve
the precision of the lateral measurements, this would have introduced
significant overhead in the manual segmentation process, with diminishing
returns given the spatial smoothing of the modeling algorithms that were
utilized.

The anterior aspect of the prostate can also be challenging to delineate,
especially in large prostates, where SNR decreases with increasing depth away
from our rectal wall imaging surface and MR images suffer from gland
heterogeneity in this region~\cite{Gupta2013}, though we had good agreement
between ultrasound and MR T2W images in the anterior-to-posterior dimension
(Figure~\ref{fig:mr_arfi_path_axes}(b), Table~\ref{tab:mr_arfi_axes_error}).

\textbf{B-mode/}ARFI imaging consistently underestimated the extent of the
prostate capsule and central gland apex-to-base dimension relative to MR T2WI
((Figure~\ref{fig:mr_arfi_path_axes}(c), Table~\ref{tab:mr_arfi_axes_error}).
In fact, it is likely the degree of \textbf{B-mode/}ARFI underestimation
relative to the actual apex-to-base prostate length is even greater than
suggested by the MR comparison as this was the dimension with the worst spatial
resolution in MR imaging, with a typical MR T2WI slice thickness of $\sim$3 mm
for these studies.  While higher-resolution MR images could be obtained and
analyzed for more precise comparisons in this imaging dimension, such data were
not available for this study.

### 2014-04-24 fig_mr_arfi_path_axes.tex
draft edits and spelling
modified format and cover letter for Ultrasonic Imaging submission
updated text to explicitely state that B-mode images were used with ARFI images for all of the total gland / capsule approximations

\begin{figure}[htb!]
\centering
\begin{tabular}{ccc}
%\includegraphics[width=0.3\linewidth]{figs/Lateral-to-Lateral} &
%\includegraphics[width=0.3\linewidth]{figs/Anterior-to-Posterior} &
%\includegraphics[width=0.3\linewidth]{figs/Apex-to-Base} \\
%(a) & (b) & (c) \\
\includegraphics[width=0.3\linewidth]{figs/Imaging_Lateral-to-Lateral} &
\includegraphics[width=0.3\linewidth]{figs/Imaging_Anterior-to-Posterior} &
\includegraphics[width=0.3\linewidth]{figs/Imaging_Apex-to-Base} \\
(a) & (b) & (c) \\
%(d) & (e) & (f) \\
\end{tabular}
\caption{Measurements of the prostate dimensions along the three standard
    anatomic axes: lateral-to-lateral (a), anterior-to-posterior (b) and
    apex-to-base (c).  The correlation between the MR and ARFI imaging axis
    measurements was performed in each orientation for the total gland (red
    crosses) and central gland (blue circles).  The black dashed-line represents
    the projection of perfectly-correlated measurements between imaging and
    patholoy.  The over-/under-estimation of each imaging modality relative to
    gross pathology and each other is summarized in
    Table~\ref{tab:mr_arfi_axes_error}.} 
\label{fig:mr_arfi_path_axes}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{tabular}{ccc}
%\includegraphics[width=0.3\linewidth]{figs/Lateral-to-Lateral} &
%\includegraphics[width=0.3\linewidth]{figs/Anterior-to-Posterior} &
%\includegraphics[width=0.3\linewidth]{figs/Apex-to-Base} \\
%(a) & (b) & (c) \\
\includegraphics[width=0.3\linewidth]{figs/Imaging_Lateral-to-Lateral} &
\includegraphics[width=0.3\linewidth]{figs/Imaging_Anterior-to-Posterior} &
\includegraphics[width=0.3\linewidth]{figs/Imaging_Apex-to-Base} \\
(a) & (b) & (c) \\
%(d) & (e) & (f) \\
\end{tabular}
\caption{Measurements of the prostate dimensions along the three standard
    anatomic axes: lateral-to-lateral (a), anterior-to-posterior (b) and
    apex-to-base (c).  The correlation between the MR and B-mode/ARFI imaging
    axis measurements was performed in each orientation for the total gland
    (red crosses) and central gland (blue circles).  \textbf{B-mode images were
        used to estimate the total gland volume, and ARFI images were used to
        estimate the central glands.} The black dashed-line represents the
    projection of perfectly-correlated measurements between imaging and
    pathology.  The over-/under-estimation of each imaging modality relative to
    gross pathology and each other is summarized in
    Table~\ref{tab:mr_arfi_axes_error}.} 
\label{fig:mr_arfi_path_axes}
\end{figure}

### 2014-04-24 fig_mr_arfi_volumes.tex
Stephen's comments
modified format and cover letter for Ultrasonic Imaging submission
updated text to explicitely state that B-mode images were used with ARFI images for all of the total gland / capsule approximations

\begin{figure}[htb!]
\centering
\begin{tabular}{ccc}
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_volumes} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_total_linreg} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_central_linreg} \\
(a) CG:PZ Volume & (b) Total Gland Volume & (c) Central Gland Volume \\
\end{tabular}
\caption{Comparison of MR and ARFI zonal anatomy volume estimates from
    manually-segmented images.  Total prostate gland volumes ranged from
    19.6--71.0 cm$^3$ based on MR image models (a), with a moderate correlation
    between MR and ARFI imaging for both the total gland volume (R$^2$ =
    \MRarfiVolTotalRsq, (b)) and the central gland (R$^2$ =
    \MRarfiVolCentralRsq, (c)).  The ARFI total gland volumes had a positive
    bias compared with the MR volumes (\MRarfiVolTotalMeanDiff~$\pm$
    \MRarfiVolTotalStdDiff\% (b)), while the ARFI central zone volumes were on
    average more similar (\MRarfiVolCentralMeanDiff~$\pm$
    \MRarfiVolCentralStdDiff\%, (c)), but with some significant variability
    between study subjects.  Table~\ref{tab:mr_arfi_volumes} contains the
    individual volume estimates for the total prostate and central glands.}
\label{fig:mr_arfi_volumes} 
\end{figure}

>>>>

\begin{figure}
\centering
\begin{tabular}{ccc}
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_volumes} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_total_linreg} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_central_linreg} \\
(a) CG:PZ Volume & (b) Total Gland Volume & (c) Central Gland Volume \\
\end{tabular}
\caption{Comparison of MR and \textbf{B-mode/}ARFI zonal anatomy volume
    estimates from manually-segmented images.  Total prostate gland volumes
    ranged from 19.6--71.0 cm$^3$ based on MR image models (a), with good
    correlation between MR and ultrasound imaging for both the total gland
    volume (R$^2$ = \MRarfiVolTotalRsq, (b)) and the central gland (R$^2$ =
    \MRarfiVolCentralRsq, (c)).  The \textbf{B-mode} total gland volumes had a
    positive bias compared with the MR volumes (\MRarfiVolTotalMeanDiff~$\pm$
    \MRarfiVolTotalStdDiff\% (b)), while the ARFI central gland volumes were on
    average more similar (\MRarfiVolCentralMeanDiff~$\pm$
    \MRarfiVolCentralStdDiff\%, (c)), but with some significant variability
    between study subjects.  Table~\ref{tab:mr_arfi_volumes} contains the
    individual volume estimates for the total prostate and central glands.}
\label{fig:mr_arfi_volumes} 
\end{figure}

### 2014-04-24 fig_mr_arfi_weight.tex
modified format and cover letter for Ultrasonic Imaging submission
updated text to explicitely state that B-mode images were used with ARFI images for all of the total gland / capsule approximations

\begin{figure}[htb!]
\centering
\begin{small}
\begin{tabular}{lll}
\includegraphics[width=0.3\linewidth]{figs/corr_path_vol_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol} \\
(a) Prostate Weight : Prostate Volume & (b) Image Volume : Prostate Weight & (c) Image Volume : Prostate Volume \\
\end{tabular}
\end{small}
%\begin{tabular}{ll}
%\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol_no4} &
%\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol_no4} \\
%(d) Image Volume : Prostate Weight (-4) & (e) Image Volume : Path Volume (-4) \\
%\end{tabular}
\caption{Tri-axial pathology measurements were used to make an ellipsoidal
    prostate volume approximation based on gross pathology axis measurements,
    which was moderately well-correlated with the excised prostate weights (a,
    R$^2$ = \pathVolWeightRsq).  T2WI MR (blue, X) showed a moderate
    correlation between the reconstructed volumes and prostate weight (R$^2$ =
    \weightMRrsq), while volumes reconstructed from ARFI images (green, O)
    showed weaker correlation (R$^2$ = \weightARFIrsq) (b).  Weaker
    correlations existed between both T2WI MR and ARFI image volumes and
    approximated ellipsoidal prostate pathology volumes (R$^2$ =
    \pathVolMRrsq~and \pathVolARFIrsq, respectively) (c).  There was one
    pathology specimen that had an erroneous prostate volume and weight
    recorded, which has been excluded from the linear regressions (magenta
    circles).}
\label{fig:mr_arfi_weight}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{small}
\begin{tabular}{lll}
\includegraphics[width=0.3\linewidth]{figs/corr_path_vol_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol} \\
(a) Prostate Weight : Prostate Volume & (b) Image Volume : Prostate Weight & (c) Image Volume : Prostate Volume \\
\end{tabular}
\end{small}
%\begin{tabular}{ll}
%\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol_no4} &
%\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol_no4} \\
%(d) Image Volume : Prostate Weight (-4) & (e) Image Volume : Path Volume (-4) \\
%\end{tabular}
\caption{Tri-axial pathology measurements were used to make an ellipsoidal
    prostate volume approximation based on gross pathology axis measurements,
    which was moderately well-correlated with the excised prostate weights (a,
    R$^2$ = \pathVolWeightRsq).  T2WI MR (blue, X) showed a moderate
    correlation between the reconstructed volumes and prostate weight (R$^2$ =
    \weightMRrsq), while volumes reconstructed from \textbf{B-mode} images
    (green, O) showed weaker correlation (R$^2$ = \weightARFIrsq) (b).  Weaker
    correlations existed between both T2WI MR and \textbf{B-mode} image volumes
    and approximated ellipsoidal prostate pathology volumes (R$^2$ =
    \pathVolMRrsq~and \pathVolARFIrsq, respectively) (c).  There was one
    pathology specimen that had an erroneous prostate volume and weight
    recorded, which has been excluded from the linear regressions (magenta
    circles).}
\label{fig:mr_arfi_weight}
\end{figure}

### 2014-04-24 fig_setup_annotated.tex
modified format and cover letter for Ultrasonic Imaging submission
updated text to explicitely state that B-mode images were used with ARFI images for all of the total gland / capsule approximations

\begin{figure}[htb!]
\centering
\includegraphics[width=0.75\textwidth]{figs/setup_annotated.png}
\caption{The experimental setup used for ARFI imaging in the operating suite,
    including the Siemens SC2000 scanner with the ER7B endorectal transducer
    sitting in a custom cradle of a CIVCO Micro-Touch\texttrademark stabilizer
    with optical feedback controlling a stepper motor to acquire 3D ultrasound
    imaging data \invivo.  Custom-written Python code was run on the scanner to
    trigger B-mode and ARFI imaging acquisition sequences relative to completed
    rotation increments of $\sim$1\degree.}
\label{fig:setup_annotated} 
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figs/setup_annotated.png}
\caption{The experimental setup used for \textbf{B-mode/}ARFI imaging in the
    operating suite, including the Siemens SC2000 scanner with the ER7B
    endorectal transducer sitting in a custom cradle of a CIVCO
    Micro-Touch\texttrademark stabilizer with optical feedback controlling a
    stepper motor to acquire 3D ultrasound imaging data \invivo.
    Custom-written Python code was run on the scanner to trigger B-mode and
    ARFI imaging acquisition sequences relative to completed rotation
    increments of $\sim$1\degree.}
\label{fig:setup_annotated} 
\end{figure}

### 2014-04-24 image_proc_methods.tex
updated path contraction text and image segmentation
updated text to explicitely state that B-mode images were used with ARFI images for all of the total gland / capsule approximations

\subsubsection{Ultrasound Image Segmentation and Modeling}
\Sagittal B-mode and ARFI ultrasound image stacks were segmented in 3D Slicer
\textbf{by two researchers (TJG \& ZAM)} using the \verb+draweffect+ tool to model and measure the prostate capsule and
CG volume and tri-axial dimensions (Figure~\ref{fig:arfi_segs}).  The sagittal
imaging plane was chosen for segmentation because it has a greater number of
easily identifiable anatomical structures:  seminal vesicles in the left and
right posterior base, urethra in the mid apex, surrounding fibromuscular tissue
in the anterior, and rectum in the posterior. Prostate capsule was segmented in
B-mode as this modality offers both high contrast between prostatic tissue and
surrounding peri-prostatic fat, and better SNR in the anterior capsule region
than ARFI images. ARFI images were used for CG segmentation.  Prior to
segmentation, both the B-mode and ARFI image stacks were down-sampled along the
sagittal axis to a slice thickness of 3 mm to reduce the number of
manually-segmented frames (18 vs. 360 slices / image stack) and match the MRI
slice thickness.

>>>>

\subsubsection{Ultrasound Image Segmentation and Modeling}
Sagittal B-mode and ARFI ultrasound image stacks were segmented in 3D Slicer
\textbf{by two researchers (TJG \& ZAM)} using the \verb+draweffect+ tool to
model and measure the prostate capsule and CG volume and tri-axial dimensions
(Figure~\ref{fig:arfi_segs}).  \input{bmode_arfi_coregistered} The sagittal imaging plane was chosen for
segmentation because it has a greater number of easily identifiable anatomical
structures:  seminal vesicles in the left and right posterior base, urethra in
the mid apex, surrounding fibromuscular tissue in the anterior, and rectum in
the posterior. Prostate capsule was segmented in B-mode as this modality offers
both high contrast between prostatic tissue and surrounding peri-prostatic fat,
and better SNR in the anterior capsule region than ARFI images. ARFI images
were used for CG segmentation.  Prior to segmentation, both the B-mode and ARFI
image stacks were down-sampled along the sagittal axis to a slice thickness of
3 mm to reduce the number of manually-segmented frames (18 vs. 360 slices /
image stack) and match the MRI slice thickness.

### 2014-04-24 intro.tex
updated text to explicitely state that B-mode images were used with ARFI images for all of the total gland / capsule approximations

The goal of this study is to evaluate the ability of ARFI imaging to delineate
prostate zonal anatomy, specifically central gland and total prostate gland
\invivo as compared to T2WI MR at 3T using an endorectal coil.
\input{intro_vibroelastography}
Section~\ref{sect:background} of this manuscript provides an overview of MR and
ARFI imaging in the prostate and an overall clinical motivation for prostate
imaging.  Section~\ref{sect:methods} describes the methods used to
experimentally-acquire our imaging data, process the gross pathological
specimens post radical prostatectomy, and image process our datasets.  The
results of our analysis, including gross pathology and imaging prostate axis
and volume estimates, are presented in Section~\ref{sect:results}, along with a
statistical analysis of the bias and variability associated with each imaging
modalities measurements, all of which is discussed in
Section~\ref{sect:discussion}.

>>>>

The goal of this study is to evaluate the ability of \textbf{B-mode/}ARFI
imaging to delineate prostate zonal anatomy, specifically central gland and
total prostate gland \invivo as compared to T2WI MR at 3T using an endorectal
coil.  \input{intro_vibroelastography} Section~\ref{sect:background} of this
manuscript provides an overview of MR and ARFI imaging in the prostate and an
overall clinical motivation for prostate imaging.  Section~\ref{sect:methods}
describes the methods used to experimentally-acquire our imaging data, process
the gross pathological specimens post radical prostatectomy, and image process
our datasets.  The results of our analysis, including gross pathology and
imaging prostate axis and volume estimates, are presented in
Section~\ref{sect:results}, along with a statistical analysis of the bias and
variability associated with each imaging modalities measurements, all of which
is discussed in Section~\ref{sect:discussion}.
